{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-07 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
            Each of the reference books gives a proof of the theorem. 
            But for the best consistency in notations, see Theorem 2.3 in Li and Wang \cite{li_relaxed_2025}. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

@@

@@

        \newpage

@@

            Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
            With following intermediate results the proof can be built easily. 
            Results (d)-(g) is showed at the end. 

@@

                \item[(d)] From Definition \ref{def:snapg-v2} it has the following equality 

@@

                \item [(e)] From Definition \ref{def:snapg-v2} it has: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 

@@

            \textbf{Proof of (d)}.
            \textbf{Proof of (e)}.
            \textbf{Proof of (f)}.

@@

            \textbf{Proof of (g)}.

>>>>

        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:snapg-v2} with line search routine to determine $L_k$. 
            Each of the reference books gives a proof of the theorem. 
            But for the best consistency in notations, see Theorem 2.3 in Li and Wang \cite{li_relaxed_2025}. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

@@

        % --------------------------------------------------------------------------------------------------------------

@@

        The following lemma state the relationships of the iterates generated by SNAPG-V2. 
        They are needed for the convergence proof. 
        % --------------------------------------------------------------------------------------------------------------
        \begin{lemma}[properties of the iterates]\label{lemma:snapg2-itrs-props}
            Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
            Let $\bar x \in \RR^n$.
            Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
            Then, the following are true: 
                \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
                \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item1}]
            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item2}]
        % --------------------------------------------------------------------------------------------------------------

@@

            Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
            Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
            The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next. 
            We list the following intermediate results, (d)-(g) are proved at the end of the proof. 

@@

                \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:

@@

                \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 

@@

            \begin{proof}[Proof of (f)]

@@

            \begin{proof}[Proof of (g)]
